Advantages of mixed unitary operators for quantum information processing

### 2018-12-12 decorrelation/mixed_unitaries.tex
fixing compilation issues

% ==============================================================================
% Section: Mathematical preliminaries
% ==============================================================================
\section{Mathematical preliminaries}
\label{sec:representing_quantum_gates}
Quantum gate operations are implemented by applying a sequence of classical control fields to some set of qubits. Fluctuations in the environment or imperfections in the controls can cause the state of the qubits to change in a way that is different from what was intended.  But if the gates are fairly stable with time and context, then we can describe their action on the qubit state using \emph{process matrices}, linear, Markovian maps on the state of some qubits.  When working with process matrices, it is convenient to write the system density operator using a vectorized representation, and in this article, we'll make use of the generalized Bloch vector,
\begin{equation}
  \vec \rho = \tr(\rho \vec \Sigma),
\end{equation}
where $\vec \Sigma$ is a vector of all $4^n$ $n$-qubit Pauli operators. The action of a gate is then given by the usual matrix multiplication:
\begin{equation}
  \rho \rightarrow \target\rho = \error \actual \rho.
\end{equation}
Here $\target_i$ is the target operation, $\actual$ is the actual gate as implemented, and $\error$ is the effective error channel.  
\begin{equation}
	\left( 
	\begin{array}{c|cccc}
		1 &  & \vec 0 & \\ 
		\hrule & &  &  \\
		\vec{m} &  & R &  \\
		 &  &  & 
	\end{array}
	\right)
\end{equation}

@@

\eq

% ==============================================================================
% Section: Example Mixed Unitary Processes
% ==============================================================================
\section{Example Mixed Unitary Processes}
\label{sec:mixed_unitary_processes}
There are often many possibly ways of implementing any given target quantum gate. Hastings and Campbell, for instance, consider gates compiled using the Solovey-Kitaev algorithm, for which  many approximate gate compilations are possible. By selecting from these various implementations at random, they show that the resulting quantum channel can be made to have significantly reduced coherent error. As a simple example of how this occurs, consider a scenario in which we have a single-qubit and four possible implementations of a $\pi$-pulse about the $\sigma_x$ axis. The error channels for these four implementations are themselves unitary rotations about the $\sigma_x$ axis with rotation angles of $\{-2\epsilon, -epsilon, epsilon, 2\epsilon\}$. Such a situation could appear, for instance, if there were amplitude errors on the fields used to affect the gates, and if the control could be implemented by a rotation about the positive or negative $\sigma_x$ axis.

\begin{tabular}{cccc}
	Gate & H_{\rm{eff}} & AGI & $\vert\vert\cdot\vert\vert_\diamond$ \\
	$U_{+2\epsilon}$ & $2\epsilon \sigma_x$ & $4\epsilon^2$ & $2\epsilon$\\
	$U_{+\epsilon}$ & $\epsilon \sigma_x$ & $\epsilon^2$ & $\epsilon$ \\
	$U_{-\epsilon}$ & $-\epsilon \sigma_x$ & $\epsilon^2$ & $\epsilon$ \\
	$U_{-2\epsilon}$ & $-2\epsilon \sigma_x$ & $4\epsilon^2$ & $2\epsilon$ 
\end{tabular}

Make a table of these error channels.

>>>>

% ==============================================================================
% Section: Mathematical preliminaries
% ==============================================================================
\section{Mathematical preliminaries}
\label{sec:representing_quantum_gates}
Quantum gate operations are implemented by applying a sequence of classical control fields to some set of qubits. Fluctuations in the environment or imperfections in the controls can cause the state of the qubits to change in a way that is different from what was intended.  But if the gates are fairly stable with time and context, then we can describe their action on the qubit state using \emph{process matrices}, linear, Markovian maps on the state of some qubits.  When working with process matrices, it is convenient to write the system density operator using a vectorized representation, and in this article, we'll make use of the generalized Bloch vector,
\begin{equation}
  \vec \rho = \tr(\rho \vec \Sigma),
\end{equation}
where $\vec \Sigma$ is a vector of all $4^n$ $n$-qubit Pauli operators. The action of a gate is then given by the usual matrix multiplication:
\begin{equation}
  \rho \rightarrow \target\rho = \error \actual \rho.
\end{equation}
Here $\target_i$ is the target operation, $\actual$ is the actual gate as implemented, and $\error$ is the effective error channel.

\begin{equation}
	\left(\begin{array}{c|cccc}
		1 &  & \vec0 & \\ 
		\hline & &  &  \\
		\vec{m} &  & R &  \\
		 &  &  & 
	\end{array} 	
	\right)
\end{equation}

@@

%\eq

% ==============================================================================
% Section: Example Mixed Unitary Processes
% ==============================================================================
\section{Example Mixed Unitary Processes}
\label{sec:mixed_unitary_processes}
There are often many possibly ways of implementing any given target quantum gate. Hastings and Campbell, for instance, consider gates compiled using the Solovey-Kitaev algorithm, for which  many approximate gate compilations are possible. By selecting from these various implementations at random, they show that the resulting quantum channel can be made to have significantly reduced coherent error. As a simple example of how this occurs, consider a scenario in which we have a single-qubit and four possible implementations of a $\pi$-pulse about the $\sigma_x$ axis. The error channels for these four implementations are themselves unitary rotations about the $\sigma_x$ axis with rotation angles of $\{-2\epsilon, -\epsilon, \epsilon, 2\epsilon\}$. Such a situation could appear, for instance, if there were amplitude errors on the fields used to affect the gates, and if the control could be implemented by a rotation about the positive or negative $\sigma_x$ axis.

\begin{center}

\begin{tabular}{cccc}
	Gate & $H_{\rm{eff}}$ & AGI & $\vert\vert\cdot\vert\vert_\diamond$ \\
\hline
	$U_{+2\epsilon}$ & $2\epsilon \sigma_x$ & $4\epsilon^2$ & $2\epsilon$\\
	$U_{+\epsilon}$ & $\epsilon \sigma_x$ & $\epsilon^2$ & $\epsilon$ \\
	$U_{-\epsilon}$ & $-\epsilon \sigma_x$ & $\epsilon^2$ & $\epsilon$ \\
	$U_{-2\epsilon}$ & $-2\epsilon \sigma_x$ & $4\epsilon^2$ & $2\epsilon$ 
\end{tabular}

\end{center}
Make a table of these error channels.
